CS6110: Software Verification Final Project: Formal Verification of Rust Programs with Creusot

### 2023-05-04 paper.tex
adjusted intro

\begin{abstract}
\noindent
Rust is the hottest new language in systems programming.
Its linear type system provides compile-time guarantees about memory resources and avoids race-conditions.
With an increased reliance on Rust for critical code, there's a greater need for verification tools.
Several new tools have popped up to fill this need: in particular, we are looking at Creusot, a formal verification system, and Kani, a model checker.
In our project we will be verifying code with Creusot and/or Kani.
\end{abstract}

>>>>

\begin{abstract}
\noindent
Rust is the hottest new language in systems programming.
Its linear type system provides compile-time guarantees about memory resources and avoids race-conditions.
With an increased reliance on Rust for critical code, there's a greater need for verification tools.
Several new tools have popped up to fill this need: in particular, we are looking at Creusot, a formal verification system.
In our project, we learned about and tried verifying code with Creusot.
Our experience convinced us that the project seems very useful for verifying Rust code in theory but still needs some improvement for usability. 
If nothing else, Creusot shows how to utilize Rust's unique features as well as existing theorem provers to make a compelling verification tool. 
\end{abstract}
